---
title: "Crime in India"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(dplyr)
library(plotly)
library(forcats)
library(tidyr)
library(rgeos)
library(maptools)
library(ggmap)
library(broom)
library(leaflet)
library(maps)
library(sf)
library(ggthemes)
```

```{r}
crime_2016<- read.csv("/Users/chandermohan/Desktop/Data_visualization/NCRB_CII_2017_State_Table-2.2.csv")
crime_2017<- read.csv("/Users/chandermohan/Desktop/Data_visualization/NCRB_CII_2018_State_Table2.2.csv")
crime_2018<-read.csv("/Users/chandermohan/Desktop/Data_visualization/Table_2.2A_2016 (1).csv")
colnames(crime_2016)[3] <- "ST_NM"
colnames(crime_2016)[19] <- "Total_crime_2016"
colnames(crime_2017)[3] <- "ST_NM"
colnames(crime_2017)[19] <- "Total_crime_2017"
colnames(crime_2018)[3] <- "ST_NM"
colnames(crime_2018)[19] <- "Total_crime_2018"
row_array_2016 <- crime_2016[39, -c(1,2,3,19) ]
row_array_2017 <- crime_2017[39, -c(1,2,3,19) ]
row_array_2018 <- crime_2018[39, -c(1,2,3,19) ]
#new_df <- row_array %>%
 # pivot_longer(cols = everything(), names_to = "Crime_Type", values_to = "Count")
#new_df
```

```{r}
simplified_names <- c("Murder", "Culpable_Homicide", "Dowry_Deaths", "Infanticide",
                      "Foeticide", "Attempt_Murder", "Attempt_Culpable_Homicide",
                      "Grievous_Hurt", "Kidnapping_Abduction", "Rape", "Attempt_Rape",
                      "Rioting", "Robbery", "Dacoity", "Arson")
colnames(row_array_2016) <- simplified_names

colnames(row_array_2017) <- simplified_names

colnames(row_array_2018) <- simplified_names

df_transposed_2016 <- t(row_array_2016)

# Create a new dataframe with the transposed data
df_new_2016 <- data.frame(
  Crime = row.names(df_transposed_2016),
  Count_2016 = as.numeric(df_transposed_2016),
  stringsAsFactors = FALSE
)


df_transposed_2017 <- t(row_array_2017)

# Create a new dataframe with the transposed data
df_new_2017 <- data.frame(
  Crime = row.names(df_transposed_2017),
  Count_2017 = as.numeric(df_transposed_2017),
  stringsAsFactors = FALSE
)

df_transposed_2018 <- t(row_array_2018)

# Create a new dataframe with the transposed data
df_new_2018 <- data.frame(
  Crime = row.names(df_transposed_2018),
  Count_2018 = as.numeric(df_transposed_2018),
  stringsAsFactors = FALSE
)

merged_df <- merge(df_new_2016, df_new_2017, by = "Crime")
final<- merge(df_new_2018, merged_df, by = "Crime")
final
```

```{r}

p <- ggplot(df_new_2016, aes(x = reorder(Crime, Count_2016), y = Count_2016, fill = Crime)) +
  geom_bar(stat = "identity",fill = "#377eb8",color= alpha("Black", 0.4)) +
  labs(title = "Crime Statistics", x = "Crime", y = "Count") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_y_continuous(labels = scales::comma_format()) 
  
# Print the plot
print(p)
```




```{r}
crime_2016$Total_crime_2017<-crime_2017$Total_crime_2017
crime_2016$Total_crime_2018<-crime_2018$Total_crime_2018

row_index <- which(crime_2016$`S..No` == "State")
# Remove the row at the specified index
crime_2016 <- crime_2016[-row_index, ]
#crime_2016<-crime_2016[, ]
row_index <- which(crime_2016$`S..No` == "Total All India")
# Remove the row at the specified index
crime_2016 <- crime_2016[-row_index, ]
row_index <- which(crime_2016$`S..No` == "Union Territory")
# Remove the row at the specified index
crime_2016 <- crime_2016[-row_index, ]
```

```{r}
#crime_2016<- crime_2016[-38, ]
crime_2016
```

```{r}
updatemenus <- list(
  list(
    active = 0,
    x = -.125,
    type= 'buttons',
    buttons = list(
      list(
        label = "2016",
        method = "update",
        args = list(list(visible = c(TRUE, "legendonly", "legendonly"
                                      )))),
      list(
        label = "2017",
        method = "update",
        args = list(list(visible = c("legendonly", TRUE, "legendonly"
                                    )))),
      list(
        label = "2018",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly", TRUE)))) 
     )
     )
  )


p11 <- plot_ly(data = crime_2016) %>% 
  
  add_lines(x=~ST_NM, y=~Total_crime_2016, name = "2016- Crime", visible = "TRUE") %>%
  add_lines(x=~ST_NM, y=~Total_crime_2017, name = "2017-Crime", visible = "legendonly") %>%
  add_lines(x=~ST_NM, y=~Total_crime_2018, name = "2018-Crime", visible = "legendonly") %>%
  
  layout(title = "Texas Housing Market Time Series", showlegend=TRUE,
         xaxis=list(zeroline = FALSE,title="State"),
         yaxis=list(zeroline = FALSE,title="Number of Crimes"),
         updatemenus=updatemenus)

p11
```

## Column {data-width="650"}

```{r}
national<-readShapeSpatial("/Users/chandermohan/Desktop/maps-master/States/Admin2.shp",
                          delete_null_obj=TRUE)
national_simp <- gSimplify(national, tol = .001, topologyPreserve=TRUE)
national_simp <- SpatialPolygonsDataFrame(national_simp,
                                             data=national@data)
print(object.size(national_simp), units = "MB")
names(national_simp)
names(crime_2016)
```

### Chart A

```{r}
national_simp <- gSimplify(national, tol = .001, topologyPreserve=TRUE)
national_simp <- SpatialPolygonsDataFrame(national_simp,
                                              data=national@data)
print(object.size(national_simp), units = "MB")

```

```{r}
crime_in_india_2016<-sp::merge(national_simp, crime_2016, by="ST_NM")
crime_in_india_2017<-sp::merge(national_simp, crime_2017, by="ST_NM")
crime_in_india_2018<-sp::merge(national_simp, crime_2018, by="ST_NM")

```

## Column {data-width="350"}

### Chart B

```{r}
pal <- colorNumeric(
  "RdBu",
  domain = crime_in_india_2016$Total_crime
  )
```

```{r}
map <- leaflet(crime_in_india_2016) %>%
  setView(lng =  77.4126, lat = 23.2599, zoom = 4)
map %>% addPolygons(
  fillColor = ~pal(Total_crime),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7)
```

```{r}
map1 <- leaflet(crime_in_india_2016) %>%
  setView(lng =  77.4126, lat = 23.2599, zoom = 4)
map %>% addPolygons(
  fillColor = ~pal(Total_crime),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7)
labels <- sprintf(
  "<strong>%s</strong><br/>%g Crime",
  crime_in_india_2016$ST_NM,
  crime_in_india_2016$Total_crime
) %>% lapply(htmltools::HTML)

library(htmlwidgets)
library(htmltools)

title <- tags$div(
   HTML('<h3>Total Crime in India in 2016</h3>')
 )

map1 %>% addPolygons(
  fillColor = ~pal(Total_crime),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7,
  highlight = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>%
  addLegend(pal = pal,
            values = ~Total_crime,
            opacity = 0.9, title = " Number of Crime",
            position = "bottomright",
            labFormat = labelFormat(suffix = " Crime")
            ) %>%
  addControl(title, position = "topright")
```

### Chart C

```{r}
currentYear <- 2016
currentData <- crime_in_india_2016

updatemenus <- list(
  list(
    active = 0,
    type = "buttons",
    buttons = list(
      list(
        label = "2016",
        method = "update",
        args = list(list(visible = list(TRUE, FALSE, FALSE)))
      ),
      list(
        label = "2017",
        method = "update",
        args = list(list(visible = list(FALSE, TRUE, FALSE)))
      ),
      list(
        label = "2018",
        method = "update",
        args = list(list(visible = list(FALSE, FALSE, TRUE)))
      )
    )
  )
)
actionButton("yearButton", "Change Year")
currentData <- crime_in_india_2016
current
```

```{r}
updatemenus <- list(
  list(
    active = 0,
    x = -.125,
    type= 'buttons',
    buttons = list(
      list(
        label = "2016",
        method = "update",
        args = list(list(visible = c(TRUE, "legendonly", "legendonly"
                                      )))),
      list(
        label = "2017",
        method = "update",
        args = list(list(visible = c("legendonly", TRUE, "legendonly"
                                      )))),
      list(
        label = "2018",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly", TRUE
                                    ))))
    )
  )
)
map2 <- leaflet(crime_in_india_2017) %>%
  setView(lng =  77.4126, lat = 23.2599, zoom = 4)
map2 %>% addPolygons(
  fillColor = ~pal(Total_crime),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7)
labels <- sprintf(
  "<strong>%s</strong><br/>%g Crime",
  crime_in_india_2017$ST_NM,
  crime_in_india_2017$Total_crime
) %>% lapply(htmltools::HTML)

title <- tags$div(
   HTML('<h3>Total Crime in India in 2017</h3>')
 )

map2 %>% addPolygons(
  fillColor = ~pal(Total_crime),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7,
  highlight = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>%
  addLegend(pal = pal,
            values = ~Total_crime,
            opacity = 0.6, title = " Number of Crime",
            position = "bottomright",
            labFormat = labelFormat(suffix = " Crime")
            ) %>%
  addControl(title, position = "topright")

map3 <- leaflet(crime_in_india_2018) %>%
  setView(lng =  77.4126, lat = 23.2599, zoom = 4)
map3 %>% addPolygons(
  fillColor = ~pal(Total_crime),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7)
labels <- sprintf(
  "<strong>%s</strong><br/>%g Crime",
  crime_in_india_2018$ST_NM,
  crime_in_india_2018$Total_crime
) %>% lapply(htmltools::HTML)

title <- tags$div(
   HTML('<h3>Total Crime in India in 2018</h3>')
 )

map3 %>% addPolygons(
  fillColor = ~pal(Total_crime),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7,
  highlight = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>%
  addLegend(pal = pal,
            values = ~Total_crime,
            opacity = 0.7, title = " Number of Crime",
            position = "bottomright",
            labFormat = labelFormat(suffix = " Crime")
            ) %>%
  addControl(title, position = "topright")


```

```{r}
police_case_2017<- read.csv("/Users/chandermohan/Desktop/Data_visualization/NCRB_CII_2017_State_Table-16A.5.csv")

```
```{r}


crime_2017$police_case<- police_case_2017$Number.of.Cases...Registered
row_index <- which(crime_2017$`S..No` == "State")
# Remove the row at the specified index
crime_2017 <- crime_2017[-row_index, ]
row_index <- which(crime_2017$`S..No` == "Total All India")
# Remove the row at the specified index
crime_2017 <- crime_2016[-row_index, ]
row_index <- which(crime_2017$`S..No` == "Union Territory")
# Remove the row at the specified index
crime_2017 <- crime_2017[-row_index, ]
crime_2017
```

```
```{r}
p1<-ggplot(crime_2017, aes(x = `police_case`, y = `Total_crime_2017`, label = `ST_NM`,color =`ST_NM`)) +
      geom_point() +
      geom_text(size = 3, vjust = 1.5)+
      scale_color_hue() +
      labs(title = "Relationship between Protein Cost and Carbon Emission", subtitle = "Per 20 grams of Protein across Different Protein Sources", x = "Protein Cost per 20 grams(USD)", y = "Carbon Emission(KG) per 20 grams of protein") +
  scale_x_continuous(breaks = seq(0, 3, by = 0.2))+
  scale_y_continuous(breaks = seq(0, 4, by = 0.4))+
 
  theme_bw()
p1
```









